Goal Document: Translating Typing Rules into JastAdd

### 2023-02-09 GoalDocument.tex
goaldoc: Add approximate timeframes for each step

The timeline for the project is spread out over 20 weeks, from now until the beginning of June.
The following steps are planned:
\begin{itemize}
  \item Define an input language and handle parsing
  \item Implement the basics required for simply typed lambda calculus
  \item Implement as many additional language features as time allows
  \item Evaluation
  \item Finalise the thesis document, starting around the end of April %(collect bullet points throughout and organise them but don't write text)
\end{itemize}

>>>>

The timeline for the project is spread out over 20 weeks, from now until the beginning of June.
The following steps are planned, with approximate timeframes:
\begin{itemize}
  \item Define an input language and handle parsing, 2 weeks
  \item Implement the basics required for simply typed lambda calculus, 2 weeks
  \item Implement as many additional language features as time allows, 8 weeks
  \item Evaluation, 2 weeks
  \item Finalise the thesis document, 6 weeks %(collect bullet points throughout and organise them but don't write text)
\end{itemize}
